### 2021-04-15 input/introduction.tex
introduction: partition ok but needs to add more content regarding the AS-cast part, help welcome

There is an ongoing evlution of storing data from the cloud to the
edges of the network. Either because it is where it has been created
and it is too expensive to be transmitted through the network, or
because it has been replicated to bring data closer to the end users
~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, the design and the development of building
blocks to manage data sets across Edge infrastructures have been
investigated for the last few years \cite{confais2017performance,
  confais2017object, fogstore, hasenburg2020towards}.  Although these systems,
provide good properties such as favouring network traffic confinement
by writting data locally, determining the location where to get the
content might be more expensive than retrieving the content itself.
%
Indeed, those systems, when not using a centralized index stored in a
Cloud, rely on a Distributed Hash Table (DHT) across the different
peers composing the infrastructure: When a client wants to access a
specific content, it has to perform a request to a first node to
determine from which site it will retrieve the content. Once it has
retrieved the content from the location it selected, a local replica
is created to improve the performance for future accesses and the
server in charge of maintaining the index is updated to reflect this
new location.
%
Accessing a remote node to find the location of an object (or one of
its copies) has many drawbacks: (i) The \textit{lookup penalty:} the
network latency to reach this remote node incurs an additional delay
to get the object, before being able to start its
downloading~\cite{asrese2019measuring, doan2019tracing}, (ii)
Answering external queries increases the load on the remote node,
potentially impacting its performance, (iii) It prevents nodes to
access objects in case of network partitioning: if the node in charge
of maintaining the object locations is isolated from the rest of the
infrastructure, nodes cannot access the object replicas even if some
would be reachable.

A simple way to tackle the aforementioned limitations would be to
maintain an index of all replicas on each node composing the
system. In addition to being complicated \TODO{impossible} for large-scale
systems, maintaining such a global index on each node is useless as there
is no interest to inform a node of the creation of a replica at the
opposite of the network (each node trying to get content from the closest node).
%
In this paper, we propose to limit the broadcast of creation/deletions
of replicas only to a subset of the nodes composing the
infrastructures.  Concretely, our protocol, entitled \NAME, transmits
messages from peer to peer until a certain condition is reached. In
the current scenario, the stop condition is related to the distance to
the nearest copy: if the message that a node receives indicates an
object has a longer distance than that which the node knows then the
transfer of the message is useless and so stopped.

@@

\TODO{add a paragraph on possible usage of the protocol in other use-cases.}

>>>>

There is an ongoing evlution of storing data from the cloud to the
edges of the network. Either because it is where it has been created
and it is too expensive to be transmitted through the network, or
because it has been replicated to bring data closer to the end users
~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, the design and the development of building
blocks to manage data sets across Edge infrastructures have been
investigated for the last few years \cite{confais2017performance,
  confais2017object, fogstore, hasenburg2020towards}.  Although these
systems, provide good properties such as favouring network traffic
confinement by writting data locally and replicating contents
according to the effective needs, determining the location where to
get the content might be more expensive than retrieving the content
itself.
%
Indeed, those systems, when not using a centralized index stored in a
Cloud, rely on a Distributed Hash Table (DHT) across the different
nodes composing the infrastructure: When a client wants to access a
specific content, it has to perform a request to a remote process to
determine from which node(s) it will retrieve the content.  Once it has
retrieved the content, a local replica
is created to improve the performance for future accesses and the
process in charge of maintaining the index is contacted once again to reflect this
new location.
%

%This strategy has two majors drawbacks :
%\begin{itemize}
%  \item (i) the lookup penalty: the network latency to reach this
%    remote node incurs an additional delay~\cite{asrese2019measuring,
%      doan2019tracing} to get the object before
%    being able to start its downloading ;
%  \item (ii) the selection of the node(s) from which the content is
%    returned: due to the lack of information that would allow the  a request to each process storing a
%%    replica is perfomed in
%\end{itemize}

Such a protocol contradicts with the objective of Edge
infrastructures that aims at reducing the impact of the
latency as well as the volume of data passing through the network:
\begin{itemize}
  \item In addition to hot spot and partitioning issues, accessing a
    remote node to find the location(s) of a content incurs an
    additional delay~\cite{asrese2019measuring, doan2019tracing} to
    get the object, before being able to start its downloading.
  \item There is no information to select the ``best'' node among the
     possible candidates from which the content  could be
     retrieved. This results in parallel requests performed by the client node to
     each candidate with the goal of retrieving the content as efficient
     as possible.
\end{itemize}

A ``simple'' way to tackle the aforementioned limitations would be to
maintain on each node composing the infrastructure and for each
content, an index of all replicas (and their ``distance'').  In such
an approach, each time a new replica is created or deleted, a message
is broadcasted from the node that performed the operation (\ie the
source) to all nodes, increasing the distance information at each hop.
%
In addition to being complicated for large-scale systems, maintaining
a global view on each node is useless as there is no interest to
inform a node of the creation/removal of a replica at the opposite of
the network (each node trying to get content from the ``closest''
node).  In other words, the broadcast should be limited to a partition
of the infrastructure, (\ie the subset of nodes that has to update the
current location for this particular content). Obviously, these
partitions depend and evolve according to concurrent operations made by nodes and
dynamic changes in the infrastructure (network failures, node
apparitions/leaves).

In this paper, we propose a first implementation of such a protocol.
Entitled \NAME, our protocol relies on a primitive that forwards
messages until a certain condition is reached, \ie the scope. The
scope is defined by a boolean function (predicate) that returns
whether a message should be propagated or not around its
broadcaster. In the current scenario, the stop condition is related to
the distance to the nearest replica : if the message that a node receives
indicates a content has a longer distance than that which the node
knows then the transfer of the message is useless and so stopped.
%

This primitive is used to communicate with the different nodes
according to four events: creation/removal of a replica and node
apparitions/leaves. \TODO{network failures is considered as a node leave?}

@@

% TODO : Use cases
While we use the distance to the closest copy in this paper, It is
notewothy that other scopes can be envisioned according to the
use-cases.  For instance, the location of a city in order to broadcast
message to all nodes in the city.  This requires nodes to store and
maintain their city location in their local state. Nodes stop
delivering and forwarding their received messages when they come from
a different city. Such a predicate can be complexified in order to
broadcast messages to all nodes in the city plus neighboring
cities. This requires nodes to overload forwarded messages the first
time they reach another city. The predicate checks if messages already
reached two distinct cities before delivery.  The predicate can even
be piggypack within the message and so be different for each
message.\TODO{Complete the use-cases}
